Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-03-29 src-latex/parts/00-abstract.tex
Move fig. 1 ref from abstract to introduction

% !TeX root = ../main-paper.tex
Named entity recognition (NER) is a necessary step in many pipelines targeting historical documents.
Indeed, such natural language processing techniques identify which class each text token belongs to,
e.g. ``person name'', ``location'', ``number''.
Introducing a new public dataset built from 19th century French directories,
we first assess how noisy modern, off-the-shelf OCR are.
Then, we compare modern CNN- and Transformer-based NER techniques
which can be reasonably used in the context of historical document analysis.
We measure their requirements in terms of training data,
the effects of OCR noise on their performance,
and show how Transformer-based NER can benefit from unsupervised pre-training 
and supervised fine-tuning on noisy data (\cref{fig.pipeline-overview}).
Results can be reproduced using resources available at \url{https://github.com/soduco/paper-ner-bench-das22}.
% The latest version of is paper can be obtained at \url{https://arxiv.org/abs/xxxx.xxxxx}.

>>>>

% !TeX root = ../main-paper.tex
Named entity recognition (NER) is a necessary step in many pipelines targeting historical documents.
Indeed, such natural language processing techniques identify which class each text token belongs to,
e.g. ``person name'', ``location'', ``number''.
Introducing a new public dataset built from 19th century French directories,
we first assess how noisy modern, off-the-shelf OCR are.
Then, we compare modern CNN- and Transformer-based NER techniques
which can be reasonably used in the context of historical document analysis.
We measure their requirements in terms of training data,
the effects of OCR noise on their performance,
and show how Transformer-based NER can benefit from unsupervised pre-training 
and supervised fine-tuning on noisy data.
Results can be reproduced using resources available at \url{https://github.com/soduco/paper-ner-bench-das22}.
% The latest version of is paper can be obtained at \url{https://arxiv.org/abs/xxxx.xxxxx}.
